### 2013-03-24 doc/sosp13/communication.tex
minor edits
edits/comments on new aggregator

\section{Communication}\label{sec:communication}

@@

Grappa’s lower networking layer aggregates the upper layer’s messages to
improve performance. Commodity networks including infiniband achieves their
peak bisection bandwidth only when the packet sizes are relatively large ---
on the order of multiple kilobytes. The reason for this discrepancy is the
combination of overheads associated with handling each packet (in terms of
bytes that form the actual packet, processing time at the card and processing
on the CPU within the driver stack).

@@

>>>>

\section{Communication Support}
\label{sec:communication}

@@

Grappa’s lower networking layer aggregates the upper layer’s messages to
improve performance. As mentioned earlier, commodity networks including
InfiniBand achieves their peak bisection bandwidth only when the packet sizes
are relatively large --- on the order of multiple kilobytes. The reason for
this discrepancy is the combination of overheads associated with handling each
packet (in terms of bytes that form the actual packet, processing time at the
card and processing on the CPU within the driver stack).

@@

% there is a message pointer list in each core. this list has as many entries
% as the number of cores in the system. each entry is another list of message
% with that destination.

% each core in a node is responsible for a set of nodes in the system

% cores in a node share a region of memory

% network buffers also reside in this shared region of memory

% messages ptrs also contain prefetching information to speed up assembling message in the buffer.

% there are as many sending workers in a core as the number of nodes it is responsible for.
